---
title: "shiny_maps"
author: "Alexander Stejskal"
date: "February 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
library(leaflet)
library(tmap)
library(plotly)
library(leaflet)
library(htmltools)
library(readxl)
#library(editData)
#library(forcats)
#library(dplyr)
```


```{r}
#house_stats <- read_excel("~/GOT/GOT_R/shiny_maps/house_stats.xlsx")

#battle_location <- read_excel("~/GOT/GOT_R/shiny_maps/battle_location.xlsx")

battle_location_map2 <- read_excel("battle_location_map2.xlsx")

```



```{r}
got_region <- st_read(dsn = ".", layer = "Political")
```



```{r}
got_region$name <- as.character(got_region$name)

got_region$name <- ifelse(is.na(got_region2$name),
                           'Beyond the Wall', got_region$name)

got_region %>% 
  replace_na(list(name = "Beyond the Wall"))
 ```



```{r}
region <- got_region %>% 
  dplyr::select(name)

plot(region)
```


```{r}
region_df <- full_join(got_region, battle_location_map2)


```


House dataframes
```{r}

house <- region_df %>% 
  dplyr::select(name, Baratheon) %>% 
  replace_na(list(name = "Beyond the Wall", Baratheon = "0"))

df_baratheon$Baratheon <- as.numeric(as.character(df_baratheon$Baratheon))







df_baratheon <- region_df %>% 
  dplyr::select(name, Baratheon) %>% 
  replace_na(list(name = "Beyond the Wall", Baratheon = "0"))

df_baratheon$Baratheon <- as.numeric(as.character(df_baratheon$Baratheon))

df_bolton <- region_df %>% 
  dplyr::select(name, Bolton) %>% 
    replace_na(list(name = "Beyond the Wall", Bolton = "0"))
df_bolton$Bolton <- as.numeric(as.character(df_bolton$Bolton))

df_frey <- region_df %>% 
  dplyr::select(name, Frey) %>% 
    replace_na(list(name = "Beyond the Wall", Frey = "0"))
df_frey$Frey <- as.numeric(as.character(df_frey$Frey))

df_glover <- region_df %>% 
  dplyr::select(name, Glover) %>% 
    replace_na(list(name = "Beyond the Wall", Glover = "0"))
df_glover$Glover <- as.numeric(as.character(df_glover$Glover))

df_greyjoy <- region_df %>% 
  dplyr::select(name, Greyjoy) %>% 
    replace_na(list(name = "Beyond the Wall", Greyjoy = "0"))
df_greyjoy$Greyjoy<- as.numeric(as.character(df_greyjoy$Greyjoy))

df_karstark <- region_df %>% 
  dplyr::select(name, Karstark) %>% 
    replace_na(list(name = "Beyond the Wall", Karstark = "0"))
df_karstark$Karstark <- as.numeric(as.character(df_karstark$Karstark))

df_lannister <- region_df %>% 
  dplyr::select(name, Lannister) %>% 
    replace_na(list(name = "Beyond the Wall", Lannister = "0"))
df_lannister$Lannister <- as.numeric(as.character(df_lannister$Lannister))

df_mormont <- region_df %>% 
  dplyr::select(name, Mormont) %>% 
    replace_na(list(name = "Beyond the Wall", Mormont = "0"))
df_mormont$Mormont <- as.numeric(as.character(df_mormont$Mormont))

df_stark <- region_df %>% 
  dplyr::select(name, Stark) %>% 
    replace_na(list(name = "Beyond the Wall", Stark = "0"))
df_stark$Stark <- as.numeric(as.character(df_stark$Stark))

df_tully <- region_df %>% 
  dplyr::select(name, Tully) %>% 
    replace_na(list(name = "Beyond the Wall", Tully = "0"))
df_tully$Tully <- as.numeric(as.character(df_tully$Tully))

df_tyrell <- region_df %>% 
  dplyr::select(name, Tyrell) %>% 
    replace_na(list(name = "Beyond the Wall", Tyrell = "0"))
df_tyrell$Tyrell <- as.numeric(as.character(df_tyrell$Tyrell))
```



```{r}

mytext=paste("Region: ", df_stark$name, "<br/>", "# of battles: ", df_stark$Stark)%>% 
  lapply(htmltools::HTML)

mybins = c(0,1,2,3,4,5,6,7)
pal1 = colorBin( palette="YlOrBr", domain = df_stark$Stark, na.color="gray", bins=mybins)

pal2 <- colorNumeric(
 palette = "Blues",
  domain = df_stark$Stark)



```


Leaflet test - Stark
```{r}

test_leaflet <- leaflet(df_stark, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal2(Stark), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal2, 
             values=~Stark, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

test_leaflet
```


pal2 <- colorNumeric(
 palette = "Blues",
  domain = df_stark$Stark)

Baratheon leaflet
```{r}
mytext_bar=paste("Region: ", df_baratheon$name, "<br/>", "# of battles: ", df_baratheon$Baratheon)%>% 
  lapply(htmltools::HTML)
mybins_bar = c(0,1,2,3)
pal_bar = colorBin( palette="Blues", domain = df_baratheon$Baratheon, na.color="gray", bins=mybins_bar)

#pal_bar <- colorNumeric(
 #palette = "Blues",
  #domain = df_baratheon$Baratheon)

baratheon_leaflet <- leaflet(df_baratheon, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_bar(Baratheon), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_bar, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_bar, 
             values=~Baratheon, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

baratheon_leaflet
```


Bolton leaflet
```{r}
mytext_BOLLL = paste("Region: ", df_bolton$name, "<br/>", "# of battles: ", df_bolton$Bolton)%>% 
  lapply(htmltools::HTML)

mybins_BOLLL = c(0,1,2,3)

pal_BOLLL = colorBin( palette="Blues", domain = df_bolton$Bolton, na.color="gray", bins=mybins_BOLLL)


bolton_leaflet <- leaflet(df_bolton, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_BOLLL(Bolton), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_BOLLL, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_BOLLL, 
             values=~Bolton, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

bolton_leaflet
```


Frey leaflet
```{r}
mytext_frey = paste("Region: ", df_frey$name, "<br/>", "# of battles: ", df_frey$Frey)%>% 
  lapply(htmltools::HTML)

mybins_frey = c(0,1,2,3)

pal_frey = colorBin( palette="Blues", domain = df_frey$Frey, na.color="gray", bins=mybins_frey)


frey_leaflet <- leaflet(df_frey, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_frey(Frey), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_frey, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_frey, 
             values=~Frey, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

frey_leaflet
```



Glover leaflet
```{r}
mytext_glo = paste("Region: ", df_glover$name, "<br/>", "# of battles: ", df_glover$Glover)%>% 
  lapply(htmltools::HTML)

mybins_glo = c(0,1,2)

pal_glo = colorBin( palette="Blues", domain = df_glover$Glover, na.color="gray", bins=mybins_glo)


glover_leaflet <- leaflet(df_glover, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_glo(Glover), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_glo, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_glo, 
             values=~Glover, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

glover_leaflet
```




Greyjoy leaflet
```{r}
mytext_grey = paste("Region: ", df_greyjoy$name, "<br/>", "# of battles: ", df_greyjoy$Greyjoy)%>% 
  lapply(htmltools::HTML)

mybins_grey = c(0,1,2,3,4,5,6,7,8,9)

pal_grey = colorBin( palette="Blues", domain = df_greyjoy$Greyjoy, na.color="gray", bins=mybins_grey)


greyjoy_leaflet <- leaflet(df_greyjoy, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_grey(Greyjoy), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_grey, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_grey, 
             values=~Greyjoy, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

greyjoy_leaflet
```



Karstark leaflet
```{r}
mytext_kar = paste("Region: ", df_karstark$name, "<br/>", "# of battles: ", df_karstark$Karstark)%>% 
  lapply(htmltools::HTML)

mybins_kar = c(0,1,2)

pal_kar = colorBin( palette="Blues", domain = df_karstark$Karstark, na.color="gray", bins=mybins_kar)


karstark_leaflet <- leaflet(df_karstark, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_kar(Karstark), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_kar, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_kar, 
             values=~Karstark, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

karstark_leaflet
```



Lannister leaflet
```{r}
mytext_lan = paste("Region: ", df_lannister$name, "<br/>", "# of battles: ", df_lannister$Lannister)%>% 
  lapply(htmltools::HTML)

mybins_lan = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13)

pal_lan = colorBin( palette="Blues", domain = df_lannister$Lannister, na.color="gray", bins=mybins_lan)


lannister_leaflet <- leaflet(df_lannister, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_lan(Lannister), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_lan, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_lan, 
             values=~Lannister, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

lannister_leaflet
```



Mormont leaflet
```{r}
mytext_mor = paste("Region: ", df_mormont$name, "<br/>", "# of battles: ", df_mormont$Mormont)%>% 
  lapply(htmltools::HTML)

mybins_mor = c(0,1,2)

pal_mor = colorBin( palette="Blues", domain = df_mormont$Mormont, na.color="gray", bins=mybins_mor)


mormont_leaflet <- leaflet(df_mormont, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_mor(Mormont), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_mor, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_mor, 
             values=~Mormont, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

mormont_leaflet
```


Stark leaflet
```{r}
mytext_sta = paste("Region: ", df_stark$name, "<br/>", "# of battles: ", df_stark$Stark)%>% 
  lapply(htmltools::HTML)

mybins_sta = c(0,1,2,3,4,5,6,7)

pal_sta = colorBin( palette="YlOrBr", domain = df_stark$Stark, na.color="gray", bins=mybins_sta)


stark_leaflet <- leaflet(df_stark, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_sta(Stark), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_sta, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_sta, 
             values=~Stark, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

stark_leaflet
```


Tully leaflet
```{r}
mytext_tul = paste("Region: ", df_tully$name, "<br/>", "# of battles: ", df_tully$Tully)%>% 
  lapply(htmltools::HTML)

mybins_tul = c(0,1,2,3,4,5)

pal_tul = colorBin( palette="YlOrBr", domain = df_tully$Tully, na.color="gray", bins=mybins_tul)


tully_leaflet <- leaflet(df_tully, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_tul(Tully), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_tul, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_tul, 
             values=~Tully, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

tully_leaflet
```


Tyrell leaflet
```{r}
mytext_tyr = paste("Region: ", df_tyrell$name, "<br/>", "# of battles: ", df_tyrell$Tyrell)%>% 
  lapply(htmltools::HTML)

mybins_tyr = c(0,1,2)

pal_tyr = colorBin( palette="YlOrBr", domain = df_tyrell$Tyrell, na.color="gray", bins=mybins_tyr)


tyrell_leaflet <- leaflet(df_tyrell, options = leafletOptions(crs = leafletCRS(crsClass = "L.CRS.Simple"))) %>% 
  addPolygons(fillColor = ~pal_tyr(Tyrell), 
              stroke=TRUE, 
              fillOpacity = 0.9, 
              color="black", 
              weight=0.9,
              label = mytext_tyr, 
              labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                          textsize = "13px", direction = "auto")) %>% 
  addLegend( pal=pal_tyr, 
             values=~Tyrell, 
             opacity=1, 
             title = "Number of Battles per Region", 
             position = "bottomleft")
  

tyrell_leaflet
```



leaf <- leaflet() %>% addTiles() %>% addLegend(
  position = 'bottomright',
  colors = rgb(t(col2rgb(palette())) / 255),
  labels = palette(), opacity = 1,
  title = 'An Obvious Legend'
)

# see what it looks like with no customization
leaf

# you specify a custom style like this
#   but the legend rectanges are .legend i
#   instead of .legend .circle
library(htmltools)


# Final Map
leaflet(world_spdf) %>% 
  addTiles()  %>% 
  setView( lat=10, lng=0 , zoom=2) %>%
  addPolygons( 
    fillColor = ~mypalette(POP2005), stroke=TRUE, fillOpacity = 0.9, color="white", weight=0.3,
    highlight = highlightOptions( weight = 5, color = ~colorNumeric("Blues", POP2005)(POP2005), dashArray = "", fillOpacity = 0.3, bringToFront = TRUE),
    label = mytext,
    labelOptions = labelOptions( style = list("font-weight" = "normal", padding = "3px 8px"), textsize = "13px", direction = "auto")
  ) %>%
  addLegend( pal=mypalette, values=~POP2005, opacity=0.9, title = "Population (M)", position = "bottomleft" )



# Create a color palette with handmade bins.
mybins=c(0,10,20,50,100,500,Inf)
mypalette = colorBin( palette="YlOrBr", domain=world_spdf@data$POP2005, na.color="transparent", bins=mybins)

# Prepar the text for the tooltip:
mytext=paste("Country: ", world_spdf@data$NAME,"<br/>", "Area: ", world_spdf@data$AREA, "<br/>", "Population: ", round(world_spdf@data$POP2005, 2), sep="") %>%
  lapply(htmltools::HTML)




Baratheon map
```{r}
baratheon_map <- ggplot(df_baratheon) +
  geom_sf(aes(fill = Baratheon), color = "white", size = 0.2) +
  #scale_fill_gradient(colors = c("blue","mediumorchid1","orange")) +
  theme_minimal()

baratheon_map

```


Bolton map
```{r}
bolton_map <- ggplot(df_bolton) +
  geom_sf(aes(fill = Bolton), color = "white", size = 0.2) +
  #scale_fill_gradient(colors = c("blue","mediumorchid1","orange")) +
  theme_minimal()

bolton_map
```


Frey map
```{r}
frey_map <- ggplot(df_frey) +
  geom_sf(aes(fill = Frey), color = "white", size = 0.2) +
  #scale_fill_gradient(colors = c("blue","mediumorchid1","orange")) +
  theme_minimal()

frey_map
```


Glover map
```{r}
glover_map <- ggplot(df_glover) +
  geom_sf(aes(fill = Glover), color = "white", size = 0.2)+
  theme_minimal()

glover_map
```


Greyjoy map
```{r}
greyjoy_map <- ggplot(df_greyjoy) +
  geom_sf(aes(fill = Greyjoy), color = "white", size = 0.2) +
  theme_minimal()

greyjoy_map
```


Karstark map
```{r}
karstark_map <-ggplot(df_karstark) +
  geom_sf(aes(fill = Karstark), color = "white", size = 0.2) +
  theme_minimal()

karstark_map
```


Lannister map
```{r}
lannister_map <- ggplot(df_lannister) +
  geom_sf(aes(fill = Lannister), color = "white", size = 0.2) +
  theme_minimal()

lannister_map
```


Mormont map
```{r}
mormont_map <- ggplot(df_mormont) +
  geom_sf(aes(fill = Mormont), color = "white", size = 0.2) +
  theme_minimal()

mormont_map
```


Stark map
```{r}
stark_map <- ggplot(df_stark) +
  geom_sf(aes(fill = Stark), color = "white", size = 0.2) +
  theme_minimal()

stark_map
```


Tully map
```{r}
tully_map <- ggplot(df_tully) +
  geom_sf(aes(fill = Tully), color = "white", size = 0.2) +
  theme_minimal()

tully_map
```


Tyrell map
```{r}
tyrell_map <- ggplot(df_tyrell) +
  geom_sf(aes(fill = Tyrell), color = "white", size = 0.2) +
  theme_minimal()

tyrell_map
```


















